### 2014-04-22 Response_to_R0_Reviews.tex

\textit{This manuscripts describes exciting work demonstrating the potential relevance
of acoustic radiation force impulse (ARFI) and B-Mode ultrasound for
delineating prostate zonal anatomy dimensions and volumes in application to
prostate cancer diagnosis and treatment.  The current state of the art involves
MRI imaging, but an ultrasound-based complement would offer the benefits of
being low-cost, real-time and portable.  This work should be of great interest
to both the technically and clinically oriented UI readership.  Overall, the
manuscript is very well written, and the presented in vivo, clinical data
support the conclusions drawn. There are a few minor questions/comments for the
authors to consider before publication, which is recommended:}

\begin{itemize}

    \item \textit{An artistic rendering or other illustration of prostate
            anatomy would facilitate the readers' understanding of the
            description of prostate anatomy in section II.A.}

    We agree with this suggestion, and we have added Figure 1 to the manuscript
    that outlines the McNeals zonal anatomy of the prostaet in the coronal and
    sagittal views.

@@

    \item \textit{Pg 5, lines 109-112, are redundant with other text previously
            written in the background.}

    We agree that this text is redundant, and we have removed it from this
    section of the manuscript.

@@

    \item \textit{How would limits to ARFI resolution impact the results?}

    \item \textit{The authors explain that gross pathology weights and axis
            measurements were affected by the presence of peri-prostatic
            tissue.  Why could the peri-prostatic tissue not be differentiated
            from the prostatic tissue in histology after processing?  Wouldn't
            this enable better gold standard axis measurements?}

    \item \textit{Further to the point above, if the prostatic tissue axes
            could be measured after histological processing, could you perform
            an ROC analysis to assess ARFI/B-Mode versus MRI performance for
            axis measurement?}

    \item \textit{pg 12, line 329, change ``compliment'' to ``complement''.}

    Thank you for catching this grammatical error.  It actually existed in both
    the abstract and conclusion sections, and it has been corrected in both
    sections.

### 2014-04-22 conclusions.tex
corrected complement grammar

\section{Conclusions}
The delineation of prostate zonal anatomy in ARFI images has been compared with
the established methods for identifying zonal anatomy using MR T2W images.
Both imaging modalities showed moderate correlations between estimated organ
volume and gross pathologic weights, and ARFI:MR total prostate gland volumes
were well-correlated (R$^2$ = \MRarfiVolTotalRsq), but ARFI images yielded
prostate volumes that were, on average, larger (\MRarfiVolTotalMeanDiff\%~$\pm$
\MRarfiVolTotalStdDiff\%) than MR images, primarily due to over-estimation of
the lateral dimension of the prostate total gland (\ARFImrTotalLatLatMeanPct~
$\pm$ \ARFImrTotalLatLatStdPct\%), while differences in the other dimensions
were less significant contributors (\ARFImrTotalAntPostMeanPct~$\pm$
\ARFImrTotalAntPostStdPct\%~and \ARFImrTotalApexBaseMeanPct~$\pm$
\ARFImrTotalApexBaseStdPct\%).  The central gland volumes of ARFI and MR images
were also well-correlated (R$^2$ = \MRarfiVolCentralRsq), with minimal volume
bias between the imaging modalities, but significant variability case-to-case
(\MRarfiVolCentralMeanDiff~$\pm$ \MRarfiVolCentralStdDiff\%).  Central gland
volume differences were, again, strongly attributed to over-estimation of the
lateral dimension (\ARFImrCentralLatLatMeanPct~$\pm$
\ARFImrCentralLatLatStdPct\%), with a significant underestimation of the
apex-to-base dimension (\ARFImrCentralAntPostMeanPct~$\pm$
\ARFImrCentralAntPostStdPct\%).  Strong variability in CG volumes is believed
to be related to the extent of BPH for select cases.  Overall, ARFI imaging of
the prostate yielded prostate volumes and dimensions that were correlated with
MR T2WI estimates, with differences in the lateral and apex-to-base dimensions.
Poor image contrast between the prostate and peri-prostatic fat may be one
cause of these differences.  ARFI imaging is a promising low-cost, real-time
imaging modality that can compliment MR imaging for diagnosis, treatment
planning and management of PCa.

>>>>

\section{Conclusions}
The delineation of prostate zonal anatomy in ARFI images has been compared with
the established methods for identifying zonal anatomy using MR T2W images.
Both imaging modalities showed moderate correlations between estimated organ
volume and gross pathologic weights, and ARFI:MR total prostate gland volumes
were well-correlated (R$^2$ = \MRarfiVolTotalRsq), but ARFI images yielded
prostate volumes that were, on average, larger (\MRarfiVolTotalMeanDiff\%~$\pm$
\MRarfiVolTotalStdDiff\%) than MR images, primarily due to over-estimation of
the lateral dimension of the prostate total gland (\ARFImrTotalLatLatMeanPct~
$\pm$ \ARFImrTotalLatLatStdPct\%), while differences in the other dimensions
were less significant contributors (\ARFImrTotalAntPostMeanPct~$\pm$
\ARFImrTotalAntPostStdPct\%~and \ARFImrTotalApexBaseMeanPct~$\pm$
\ARFImrTotalApexBaseStdPct\%).  The central gland volumes of ARFI and MR images
were also well-correlated (R$^2$ = \MRarfiVolCentralRsq), with minimal volume
bias between the imaging modalities, but significant variability case-to-case
(\MRarfiVolCentralMeanDiff~$\pm$ \MRarfiVolCentralStdDiff\%).  Central gland
volume differences were, again, strongly attributed to over-estimation of the
lateral dimension (\ARFImrCentralLatLatMeanPct~$\pm$
\ARFImrCentralLatLatStdPct\%), with a significant underestimation of the
apex-to-base dimension (\ARFImrCentralAntPostMeanPct~$\pm$
\ARFImrCentralAntPostStdPct\%).  Strong variability in CG volumes is believed
to be related to the extent of BPH for select cases.  Overall, ARFI imaging of
the prostate yielded prostate volumes and dimensions that were correlated with
MR T2WI estimates, with differences in the lateral and apex-to-base dimensions.
Poor image contrast between the prostate and peri-prostatic fat may be one
cause of these differences.  ARFI imaging is a promising low-cost, real-time
imaging modality that can complement MR imaging for diagnosis, treatment
planning and management of PCa.
